\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-07 ms.tex
units
add non-members

% TODO
% - Sand, Seth, et al. Virgo: blue stars with nothing else
% - Split cluster into 2? Price-Whelan 1a and 1b?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?
% - release data for the candidate members!
% - You refer to the prior on EEP as "uniform."  While on the surface this is what it looks like in 'isochrones', that is not quite correct (and would be erroneous).  Rather, the effective prior on EEP p(E) is transformed from a Salpeter-IMF mass prior, where p(E) = p(M) * |dM/dEEP|.  Not sure the most succinct way to communicate this, but Table 1 is incorrect as is.
% - I think Figure 6 would benefit from showing the non-cluster members as well, maybe with a low alpha, to demonstrate how the model picks out the sequence like a charm.

@@

% Notebook: Figure-hierarch-results
\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{figures/hierarch-results.pdf}
\caption{The \decam\ color-magnitude diagram for sources with probabilty $>0.5$ of belonging to \clustername\ (markers).
The solid line (blue) shows the \acronym{MIST} isochrone for the median posterior sample from the hierarchical inference of the cluster population parameters, shifted to the inferred distance to \clustername, and extincted with the inferred extinction.
The dashed line (green) shows the same isochrone, shifted $\approx 0.75$ magnitudes brighter, representing the expected location of the equal-mass binary sequence of the cluster.
}
\label{fig:hierarch-iso}
\end{figure}

@@

\begin{figure}[t]
\centering
%\includegraphics[width=8cm]{gass_mlatmlon.pdf}
\includegraphics[width=8cm]{figures/gass_maps_v2.pdf}
\caption{GASS \hi column density in the region of LA II, shown in three different velocity slices (corresponding to and indicated in each panel).
The coordinate system is the Magellanic stream spherical coordinate system defined in \cite{Nidever:2008}, and the units of $L_{\rm MS}$ and $B_{\rm MS}$ are degrees.
The colorbar shows the column density of \hi in units of \todo{WHAT UNITS?}.
The red circle marks the position of \clustername.}
\label{fig:gass_maps}
\end{figure}

>>>>

% TODO
% - Sand, Seth, et al. Virgo: blue stars with nothing else
% - Split cluster into 2? Price-Whelan 1a and 1b?
% - discuss Blanco 1: high latitude, similar age, high binary fraction
% - Make a PGM for this model?
% - release data for the candidate members!
% - You refer to the prior on EEP as "uniform."  While on the surface this is what it looks like in 'isochrones', that is not quite correct (and would be erroneous).  Rather, the effective prior on EEP p(E) is transformed from a Salpeter-IMF mass prior, where p(E) = p(M) * |dM/dEEP|.  Not sure the most succinct way to communicate this, but Table 1 is incorrect as is.

@@

% Notebook: Figure-hierarch-results
\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{figures/hierarch-results.pdf}
\caption{The \decam\ color-magnitude diagram for sources with probability $>0.5$ of belonging to \clustername\ (dark, larger markers), and sources with probability $<0.5$ (lighter, smaller markers).
The solid line (blue) shows the \acronym{MIST} isochrone for the median posterior sample from the hierarchical inference of the cluster population parameters, shifted to the inferred distance to \clustername, and extincted with the inferred extinction.
The dashed line (green) shows the same isochrone, shifted $\approx 0.75$ magnitudes brighter, representing the expected location of the equal-mass binary sequence of the cluster.
}
\label{fig:hierarch-iso}
\end{figure}

@@

\begin{figure}[t]
\centering
%\includegraphics[width=8cm]{gass_mlatmlon.pdf}
\includegraphics[width=8cm]{figures/gass_maps_v3.pdf}
\caption{GASS \hi column density in the region of LA II, shown in three different velocity slices (corresponding to and indicated in each panel).
The coordinate system is the Magellanic stream spherical coordinate system defined in \cite{Nidever:2008}, and the units of $L_{\rm MS}$ and $B_{\rm MS}$ are degrees.
The colorbar shows the column density of \hi in units of $10^19~\textrm{atoms}~\textrm{cm}^{-2}$.
The red circle marks the position of \clustername.}
\label{fig:gass_maps}
\end{figure}
